Optimizing Abstract Abstract Machines

### 2012-11-12 paper/paper.tex
Unfold title.  Cut transition function code.

\title{Optimizing Abstract$^{\text 2}$ Machines}

@@

\begin{figure}
\begin{alltt}
  ;; State \(\to\) \(\Set(\)State\()\)
  (define (step \(\mstate\))
    (match \(\mstate\)
      [(ev \(\mexp\) \(\rho\) \(\msto\) \(\mkont\))
       (match \(\mexp\)
         [(var\(\superscript\mlab\) \(\mvar\))
          (for/set ((\(\mval\) (lookup \(\rho\) \(\msto\) \(\mvar\))))
            (co \(\msto\) \(\mkont\) \(\mval\)))]
         [(lit\(\superscript\mlab\) \(\mlit\)) (set (co \(\msto\) \(\mkont\) \(\mlit\)))]
         [(lam\(\superscript\mlab\) \(\mvar\) \(\mexp\)) (set (co \(\msto\) \(\mkont\) (clos \(\mvar\) \(\mexp\) \(\rho\))))]
         [(app\(\superscript\mlab\) \(\mexp\subscript0\) \(\mexp\subscript1\))
          (define-values (\(\msto'\) \(\maddr\)) (push \(\mstate\)))
          (set (ev \(\mexp\subscript0\) \(\rho\) \(\msto'\) (ar \(\mexp\subscript1\) \(\rho\) \(\maddr\))))]
         [(ife\(\superscript\mlab\) \(\mexp\subscript0\) \(\mexp\subscript1\) \(\mexp\subscript2\))
          (define-values (\(\msto'\) \(\maddr\)) (push \(\mstate\)))
          (set (ev \(\mexp\subscript0\) \(\rho\) \(\msto'\) (ifk \(\mexp\subscript1\) \(\mexp\subscript2\) \(\rho\) \(\maddr\))))])]
      [(co \(\msto\) \(\mkont\) \(\mval\))
       (match \(\mkont\)
         ['mt (set (ans \(\msto\) \(\mval\)))]
         [(ar\(\superscript\mlab\) \(\mexp\) \(\rho\)) (set (ev \(\mexp\) \(\rho\) \(\msto\) (fn \(\mval\) l)))]
         [(fn\(\superscript\mlab\) \(\mval'\))
          (for/set ((\(\mkont\) (get-cont \(\msto\) l)))
            (ap \(\msto\) \(\mval'\) \(\mval\) \(\mkont\)))]
         [(fi\(\superscript\mlab\) c a \(\rho\))
          (for/set ((k (get-cont \(\msto\) l)))
            (ev (if v c \(\maddr\)) \(\rho\) \(\msto\) \(\mkont\)))])]
      [(ap \(\msto\) fun \(\maddr\) \(\mkont\))
       (match fun
         [(clos l \(\mvar\) \(\mexp\) \(\rho\))
          (define-values (\(\rho'\) \(\msto'\)) (bind \(\mstate\)))
          (set (ev \(\msto'\) \(\mexp\) \(\rho'\) \(\mkont\)))]
         [(op \(\mop\))
          (for*/set ((\(\mkont\) (get-cont \(\msto\) l))
                     (\(\mval\) (\(\interpdelta\) \(\mop\) \(\mval\))))
            (co \(\msto\) \(\mkont\) \(\mval\)))]
         [_ (set)]))]))
\end{alltt}
\caption{Implementation of machine transition relation.}
\end{figure}

>>>>

\title{Optimizing Abstract Abstract Machines}

@@

%% \begin{figure}
%% \begin{alltt}
%%   ;; State \(\to\) \(\Set(\)State\()\)
%%   (define (step \(\mstate\))
%%     (match \(\mstate\)
%%       [(ev \(\mexp\) \(\rho\) \(\msto\) \(\mkont\))
%%        (match \(\mexp\)
%%          [(var\(\superscript\mlab\) \(\mvar\))
%%           (for/set ((\(\mval\) (lookup \(\rho\) \(\msto\) \(\mvar\))))
%%             (co \(\msto\) \(\mkont\) \(\mval\)))]
%%          [(lit\(\superscript\mlab\) \(\mlit\)) (set (co \(\msto\) \(\mkont\) \(\mlit\)))]
%%          [(lam\(\superscript\mlab\) \(\mvar\) \(\mexp\)) (set (co \(\msto\) \(\mkont\) (clos \(\mvar\) \(\mexp\) \(\rho\))))]
%%          [(app\(\superscript\mlab\) \(\mexp\subscript0\) \(\mexp\subscript1\))
%%           (define-values (\(\msto'\) \(\maddr\)) (push \(\mstate\)))
%%           (set (ev \(\mexp\subscript0\) \(\rho\) \(\msto'\) (ar \(\mexp\subscript1\) \(\rho\) \(\maddr\))))]
%%          [(ife\(\superscript\mlab\) \(\mexp\subscript0\) \(\mexp\subscript1\) \(\mexp\subscript2\))
%%           (define-values (\(\msto'\) \(\maddr\)) (push \(\mstate\)))
%%           (set (ev \(\mexp\subscript0\) \(\rho\) \(\msto'\) (ifk \(\mexp\subscript1\) \(\mexp\subscript2\) \(\rho\) \(\maddr\))))])]
%%       [(co \(\msto\) \(\mkont\) \(\mval\))
%%        (match \(\mkont\)
%%          ['mt (set (ans \(\msto\) \(\mval\)))]
%%          [(ar\(\superscript\mlab\) \(\mexp\) \(\rho\)) (set (ev \(\mexp\) \(\rho\) \(\msto\) (fn \(\mval\) l)))]
%%          [(fn\(\superscript\mlab\) \(\mval'\))
%%           (for/set ((\(\mkont\) (get-cont \(\msto\) l)))
%%             (ap \(\msto\) \(\mval'\) \(\mval\) \(\mkont\)))]
%%          [(fi\(\superscript\mlab\) c a \(\rho\))
%%           (for/set ((k (get-cont \(\msto\) l)))
%%             (ev (if v c \(\maddr\)) \(\rho\) \(\msto\) \(\mkont\)))])]
%%       [(ap \(\msto\) fun \(\maddr\) \(\mkont\))
%%        (match fun
%%          [(clos l \(\mvar\) \(\mexp\) \(\rho\))
%%           (define-values (\(\rho'\) \(\msto'\)) (bind \(\mstate\)))
%%           (set (ev \(\msto'\) \(\mexp\) \(\rho'\) \(\mkont\)))]
%%          [(op \(\mop\))
%%           (for*/set ((\(\mkont\) (get-cont \(\msto\) l))
%%                      (\(\mval\) (\(\interpdelta\) \(\mop\) \(\mval\))))
%%             (co \(\msto\) \(\mkont\) \(\mval\)))]
%%          [_ (set)]))]))
%% \end{alltt}
%% \caption{Implementation of machine transition relation.}
%% \end{figure}
